Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 paper/15min-presentation/15min-presentation.tex

\documentclass{beamer}
\usepackage[utf8]{inputenc}

@@

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}
%---------------------------------------------------------

\section{First section}

%---------------------------------------------------------
%Changing visivility of the text
\begin{frame}
\frametitle{Sample frame title}
This is a text in second frame. For the sake of showing an example.

\begin{itemize}
    \item<1-> Text visible on slide 1
    \item<2-> Text visible on slide 2
    \item<3> Text visible on slides 3
    \item<4-> Text visible on slide 4
\end{itemize}
\end{frame}

@@

%---------------------------------------------------------
%Example of the \pause command
\begin{frame}
In this slide \pause

@@

And finally everything will be there
\end{frame}
%---------------------------------------------------------

\section{Second section}

%---------------------------------------------------------
%Highlighting text
\begin{frame}
\frametitle{Sample frame title}

@@

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Two columns
\begin{frame}
\frametitle{Two-column slide}

@@

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}
%---------------------------------------------------------

>>>>

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\setbeamertemplate{navigation symbols}{}

@@

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Motivation}
\textbf{Clean Air}

\begin{itemize}
    \item The Clean Air Act (1970) established National Ambient Air Quality Standards
    (NAAQS) for US counties
    \item Either "attainment" or "non-attainment", penalties/forced adoption
    \item Minimum requirement of 75\% of readings, per quarter
    \item Air quality can change quickly
    \item Monitor shutoffs are common
\end{itemize}
\vspace{2em}
\textbf{Research Questions}
\begin{itemize}
\item How biased are EPA monitor-based measures of local air quality?
\item Does this bias significantly change NAAQS attainment status?
\end{itemize}

\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\begin{frame}
\frametitle{EPA National Ambient Air Quality Standards Monitors}

\includegraphics[width=\textwidth]{output/figures/epa/combined_uc_cali_epa.png}
\end{frame}

@@

%---------------------------------------------------------
%Example of the \pause command
\begin{frame}
\frametitle{National Ambient Air Quality Standards for PM2.5}
Two standards for assessing compliance for ambient PM2.5 concentrations at the location of a monitor:
\vspace{2em}

\textbf{Daily Design Value} (average)
\begin{itemize}
    \item[$\Rightarrow$] 3-year rolling average of 1-year average of daily averages
    \item[$\Rightarrow$] standard currently set at 15.0 $\mu$g/m$^3$
\end{itemize}
\vspace{1em}

\textbf{24-Hour Design Value} (98$^{th}$ percentile)
\begin{itemize}
    \item[$\Rightarrow$] 3-year rolling average of 1-year 98$^{th}$ percentile of daily averages
    \item[$\Rightarrow$] standard currently set at 35 $\mu$g/m$^3$
\end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Highlighting text
\begin{frame}
\frametitle{NAAQS Completeness Criteria for daily monitors}

\textbf{Valid day:}
minimum of 75\% hours reported  (18 hours)

\vspace{2em}
\textbf{Valid quarter:}
minimum of 75\% valid days  (22-23 days\footnote{fewer for monitors that report less frequent observations})

\vspace{2em}
\textbf{Valid quarterly design value:}
all 12 quarters in 3-year period (12 quarters)

\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Observed EPA Completeness
\begin{frame}
\frametitle{Observed Completeness of NAAQS Monitors in sample}
\includegraphics[width=0.8\textwidth]{example-image-a}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Purple Air Outdoor Monitors
\begin{frame}
\frametitle{Purple Air Outdoor Monitors}
\includegraphics[width=0.48\textwidth]{output/figures/pa/all_ca_and_15_pa_monitors.png}
\includegraphics[width=0.48]{0500}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Alternate measure of ambient air quality
\begin{frame}
\frametitle{Alternate measure of ambient air quality}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Predicting Missing EPA Data
\begin{frame}
\frametitle{Predicting Missing EPA Data}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Design Values for an EPA site
\begin{frame}
\frametitle{Calculating Design Values for an EPA Site}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Sample EPA Sites
\begin{frame}
\frametitle{Results: Sample EPA Sites}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Results: Fresno
\begin{frame}
\frametitle{Results: Fresno}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Conclusions & Discussion
\begin{frame}
\frametitle{Conclusions \& Discussion}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Future Work
\begin{frame}
\frametitle{Future Work}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Extra Tables
\begin{frame}
\frametitle{Table: }
\end{frame}
%---------------------------------------------------------

%    Examples

%%%%%%%%%%%%%%%%%% multi-slide text
\begin{frame}
In this slide \pause

@@

And finally everything will be there
\end{frame}

%%%%%%%%%%%%%%%%%% highlighting text and theorem boxes
\begin{frame}
\frametitle{NAAQS Completeness Criteria}

@@

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}

%Two columns
\begin{frame}
\frametitle{Two-column slide}

@@

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}
